---
title: "R Notebook"
output: html_notebook
---


## Requirements
1.Grab the data from the sheets
a] make use of library called "gsheets"
b] make a connection to google account
c] extract the sheet which is needed
2.Combine the data in to a dataframe called Agency Finder
a] We can combine by creating a new dataframe all of the rows from program and add only the name of organization. 
b] Create a list of service types for each program, put it in new column
c] Filtering service type


Read data from Google drive Help link:

https://stackoverflow.com/questions/47851761/r-how-to-read-a-file-from-google-drive-using-r

https://stackoverflow.com/questions/22873602/importing-data-into-r-from-google-spreadsheet#:~:text=Use%20the%20googlesheets%20package%2C%20a,can%20be%20installed%20with%20install.

https://www.r-bloggers.com/reading-data-from-google-sheets-into-r/

https://datascienceplus.com/how-to-use-googlesheets-to-connect-r-to-google-sheets/

### Docuemnt shareable link from google drive

```{r}
#https://docs.google.com/spreadsheets/d/1wXGAnRVd1vVQAit0ocTp3Ocqm1ipW51sA6lxe2iNqOg/edit?usp=sharing
```

### Using Googlesheet4 library to read the data using google drive link.

Note: using googlesheet4 as googlesheet library function are depricated from march 2020

```{r}
#library("googlesheets4")
# Parameters
  # Sheet ID for Gapminder example
#id_gapminder <- "wXGAnRVd1vVQAit0ocTp3Ocqm1ipW51sA6lxe2iNqOg"
```
## Autenticate new user
#error while authenticating the google user
```{r}
#gs4_deauth()
#read_sheet("1wXGAnRVd1vVQAit0ocTp3Ocqm1ipW51sA6lxe2iNqOg")


```

```{r}
library(googlesheets4)
```

```{r}
gs_auth(new_user = TRUE)
```


###Load Data 
```{r}
library("readxl") 
```

```{r}
Org_data <- read_excel("C:/Users/madhu/OneDrive/Documents/Ready for school, ready for life/Agency Finder/Agency Finder.xlsx", sheet = "Organization")
Program <- read_excel("C:/Users/madhu/OneDrive/Documents/Ready for school, ready for life/Agency Finder/Agency Finder.xlsx", sheet = "Program")
Loc_data <- read_excel("C:/Users/madhu/OneDrive/Documents/Ready for school, ready for life/Agency Finder/Agency Finder.xlsx", sheet = "Location")

```


### Dataframe

```{r}
View(Org_data)
View(Program)
View(Loc_data)
```


### Combine Program and Org Data
Make a new dataframe all of the rows from program and add only the name of organization
```{r}
AgencyFinder <- as.data.frame(Program)
AgencyFinder$OrganizationName <- Org_data$`Org Name`[ match(AgencyFinder$`Org ID`, Org_data$`Org ID`)]
View(AgencyFinder)

```

View Service type program table

```{r}
Service_type_program <- read_excel("C:/Users/madhu/OneDrive/Documents/Ready for school, ready for life/Agency Finder/Agency Finder.xlsx", sheet = "Service Type and Program")
View(Service_type_program)
```

### Adding service type, factor and domain

Create a list of service types for each program, put it in new column

[fucntion == program id -->find service type in junction table and create a list from it.]

1. In Agency finder dataframe,find services type id from service type and program sheet for matching program id

```{r}

AgencyFinder$ServiceTypeId<- Service_type_program$`Service Type ID`[ match(AgencyFinder$`Program ID`, Service_type_program$`Program ID`)]
View(AgencyFinder)

```

View Service Type Info table

```{r}
Service_Type_Info <- read_excel("C:/Users/madhu/OneDrive/Documents/Ready for school, ready for life/Agency Finder/Agency Finder.xlsx", sheet = "Service Type Info")
View(Service_Type_Info)
```


2.In agency finder dataframe, find service type name for matching service type id

```{r}

AgencyFinder$ServiceType<- Service_Type_Info$`Service Type`[ match(AgencyFinder$ServiceTypeId, Service_Type_Info$`Service Type ID`)]
View(AgencyFinder)

```


### Filtering service type
If domain given then list the service Factors in that domain
If given service factors list all service types in that service factor

```{r}

```




