---
title: "R Notebook"
output: html_notebook
---



```{r message=FALSE}
library(tidyverse)
library(config)
library(googlesheets4)
library(httr)
```

Waiting for authentication in browser...
Press Esc/Ctrl + C to abort
Authentication complete.
Error: Can't get Google credentials.
Are you running googlesheets4 in a non-interactive session? Consider:
  * `gs4_deauth()` to prevent the attempt to get credentials.
  * Call `gs4_auth()` directly with all necessary specifics.
See gargle's "Non-interactive auth" vignette for more details:
https://gargle.r-lib.org/articles/non-interactive-auth.html

```{r}
# Google Sheet
demo_google_sheet <- "https://docs.google.com/spreadsheets/d/1wXGAnRVd1vVQAit0ocTp3Ocqm1ipW51sA6lxe2iNqOg/"
# Service Type Tab Name
serviceTypeSheet <- "Service Type Info"
# Service Domain Tab Name
domainSheet <- "Service Domain"
# Service FactorTab Name
factorSheet <- "service Factors"

```

Error in curl::curl_fetch_memory(url, handle = handle) : Could not resolve host: sheets.googleapis.com

```{r}
demo_ServiceType <- read_sheet(demo_google_sheet, sheet = serviceTypeSheet)
```

