---
title: "R Notebook"
output: html_notebook
---

Helpful link:
https://josiahparry.com/post/2020-01-13-gs4-auth/
https://cran.r-project.org/web/packages/googlesheets4/googlesheets4.pdf
https://github.com/tidyverse/googlesheets4

```{r message=FALSE}
library(tidyverse)
library(config)
library(googlesheets4)
library(httr)
library(googledrive)
```

After running gs4_auth() in console. Received following error

Waiting for authentication in browser...
Press Esc/Ctrl + C to abort
Authentication complete.
Error: Can't get Google credentials.
Are you running googlesheets4 in a non-interactive session? Consider:
  * `gs4_deauth()` to prevent the attempt to get credentials.
  * Call `gs4_auth()` directly with all necessary specifics.
See gargle's "Non-interactive auth" vignette for more details:
https://gargle.r-lib.org/articles/non-interactive-auth.html


```{r}
# designate project-specific cache
options(gargle_oauth_cache = ".secrets")
# check the value of the option, if you like --> getting character 0
gargle::gargle_oauth_cache()
# trigger auth on purpose --> store a token in the specified cache
# a broswer will be opened ---> Received same error as above  
googlesheets4::sheets_auth()
```

```{r}
# see your token file in the cache, if you like ---> getting character 0
list.files(".secrets/")
# deauth
gs4_deauth()
```

```{r}
# sheets reauth with specified token and email address ---> Received same error
sheets_auth(
  cache = ".secrets",
  email = "madhurid@getreadyguilford.org"
  )
```
```{r}
# deauth again
sheets_deauth()

# set values in options
options(
  gargle_oauth_cache = ".secrets",
  gargle_oauth_email = "madhurid@getreadyguilford.org"
)

# run sheets auth
sheets_auth()
```
```{r}
gs4_auth(
email = gargle::gargle_oauth_email(),
path = NULL,
scopes = "https://www.googleapis.com/auth/spreadsheets",
cache = gargle::gargle_oauth_cache(),
use_oob = gargle::gargle_oob_default(),
token = NULL
)
```
#Assigning demo sheet and storing different sheets

```{r}
# Google Sheet
demo_google_sheet <- "https://docs.google.com/spreadsheets/d/1wXGAnRVd1vVQAit0ocTp3Ocqm1ipW51sA6lxe2iNqOg/"
# Service Type Tab Name
serviceTypeSheet <- "Service Type Info"
# Service Domain Tab Name
domainSheet <- "Service Domain"
# Service FactorTab Name
factorSheet <- "service Factors"

```

#After reading this sheet recived following error

Error in curl::curl_fetch_memory(url, handle = handle) : Could not resolve host: sheets.googleapis.com

```{r}
demo_ServiceType <- read_sheet(demo_google_sheet, sheet = serviceTypeSheet)
```


```{r}
library(googlesheets4)
```
```{r}
read_sheet(demo_google_sheet, sheet = serviceTypeSheet)
```

