---
title: "Service type and Factors"
output: html_notebook
---

###Load Data 

```{r}
library("readxl")
library("dplyr")
```

###Loading the data

```{r}
Org_data <- read_excel("C:/Users/madhu/OneDrive/Documents/Ready for school, ready for life/Agency Finder/Agency Finder.xlsx", sheet = "Organization")
Program <- read_excel("C:/Users/madhu/OneDrive/Documents/Ready for school, ready for life/Agency Finder/Agency Finder.xlsx", sheet = "Program")
Loc_data <- read_excel("C:/Users/madhu/OneDrive/Documents/Ready for school, ready for life/Agency Finder/Agency Finder.xlsx", sheet = "Location")
```

###Loading tables Service factor, serice type info and factor and type


```{r}
Service_factor <- read_excel("C:/Users/madhu/OneDrive/Documents/Ready for school, ready for life/Agency Finder/Agency Finder.xlsx", sheet = "Service Factors")
Service_Type <- read_excel("C:/Users/madhu/OneDrive/Documents/Ready for school, ready for life/Agency Finder/Agency Finder.xlsx", sheet = "Service Type Info")
Junction_factors_type <- read_excel("C:/Users/madhu/OneDrive/Documents/Ready for school, ready for life/Agency Finder/Agency Finder.xlsx", sheet = "Factors and Type")

```

### Creating a Dataframe with factors Table

```{r}
AgencyFinder_Factors_Type <- as.data.frame(Service_factor)
View(AgencyFinder_Factors_Type)
```
### Example factor_Id

```{r}
factor_Id <- "SF0007"
```

### Filtering Junction_factors_type table based on example factor id to get service type
```{r}
Factor_Types_1 <- Junction_factors_type
Factor_Types_2 <- filter(Factor_Types,FactorID == factor_Id )
#Factor_Types_filter <- filter(Factor_Types,Factor_Types$FactorID=="SF0007") ---> Introducing NAN and time series output
Factor_Types_3 <- left_join(Factor_Types_2,Service_Type, by='Service Type ID')
```

#create vector of service type names
```{r}
Factor_Types_3$`Service Type`
```

### Seperate service type using ,

```{r}
paste(Factor_Types_3$`Service Type`, collapse = ", ")

```

### Define a function that automates the above code.

```{r}
Func_factor_type <- function(factor_Id){
  factors_df = Junction_factors_type
  
  factors_df <- factors_df %>% 
    filter(`FactorID`== factor_Id) %>% 
    left_join(Service_Type, by = 'Service Type ID')
  
  a = as.vector(factors_df$`Service Type`)
  
  
 return( paste0(a, collapse = ";  "))
}
```

### Testing Function

```{r}
Func_factor_type('SF0007')
```

```{r}
paste0(Func_factor_type('SF0007'), collapse = ", ")
```
### Creating a test factor dataframe

```{r}
test_Factors <- Service_factor
```

### Vectorizing the function

```{r}
test_factor_list <-Vectorize(Func_factor_type)

```

### Passing a vector list of factor to the function to fetch the list of service types

```{r}
test_Factors <- test_Factors %>% 
  mutate(ServiceTypes = test_factor_list(test_Factors$`Service Factor ID`))
```


