---
title: "Week 1: Star Wars API R project"
output: html_notebook

---
Requirements:

1. Pull the data from Star wars API

a)R library used for submitting http request to web service API and parsing the content in R are httr and jsonlite

2. Person,Planets and films as endpoint to create joined dataframe

a) Need to fetch 3 endpoints in R studio i.e people, planets and films and combine them into one dataframe


3. Endproduct will be a datafrane of 10 rows of characters with basic fields, name of home planet and name of director in first film in which they appear.Assume that first film with lowest API id. 

a)10 fields will be : Name, Height, Mass, Hair_color, Skin_color, Birth_year, gender, homeworld(planet), director(film)


1] Loading library to sent API request and parse the content 

```{r}
library(tidyverse) 
library(dplyr)
library(httr) #for api request
library(jsonlite) #Handling json data

```

2] Store data for each endpoint in different variables.
Path for each endpoint is mentioned in the API documentation.
Link for the StarWars API: https://swapi.dev/
```{r}
People <- "https://swapi.dev/api/people/"
Planets <- "https://swapi.dev/api/planets/"
Films <- "https://swapi.dev/api/films/"
```
3] Building a API request and submit it. Using get function from httr package for each endpoint to get the request from the API

```{r}
request_people <- GET(People)
request_Planets <- GET(Planets)
request_Films <- GET(Films)

```

4] Check the status code for each request endpoints

Note: Status code of 200 indicates if the request is sucessfull and here we need to check if the API returned an error or not. Status code for error is 404.

```{r}
request_people$status_code
request_Planets$status_code
request_Films$status_code
```
Here we have received status code of 200 for all our endpoints.

5]Data we have received is in Json format we need to parse or handle this json data 

```{r}
request_people
```
6] Parsing the content from server to json format then converting it to dataframe format in r using rbind
```{r}
People_json <- fromJSON(People)
People_data <- do.call(rbind, People_json)
People_data


Planet_json <- fromJSON(Planets)
Planet_data <- do.call(rbind, Planet_json)
Planet_data


Films_json <- fromJSON(Films)
Films_data <-do.call(rbind,Films_json)
Films_data
```
7] Viewing the Planet_data, People_data and Film_data dataframes
 
```{r}
View(Planet_data)
View(People_data)
View(Films_data)
```

8] In People_data dataframe we want a new column called planet id which will store the id of Planet_data dataframe so id is extracted from the homeworld column which has planet endpoint api mentioned in the column.

Helpful link
https://stackoverflow.com/questions/49628339/extracting-parameter-from-url-in-r

```{r}
People_data$PlanetId <- gsub("[^0-9]", "", People_data$homeworld)
```

9] In Planet_data create a new column to store the extract id from url column.

```{r}
Planet_data$Id <- gsub("[^0-9]", "", Planet_data$url)
```

10] First two rows in the people dataframe id are invalid so replacing it with NA values

```{r}
People_data$PlanetId[1] <- NA
People_data$PlanetId[2] <- NA

```


11] First two rows in the planet dataframe id are invalid so replacing it with NA values


```{r}
Planet_data$Id[1] <- NA  
Planet_data$Id[2] <- NA  


```




