---
title: "Character Sheet"
output: html_document
params:
  Id: 3
  Char_name: "Luke"
  Height: "172"
---
### Requirements:

1. Pull the data from Star wars API

a) R library used for submitting http request to web service API and parsing the content in R are httr and jsonlite

2. Person,Planets and films as endpoint to create joined dataframe

a) Need to fetch 3 endpoints in R studio i.e people, planets and films and combine them into one dataframe


3. Endproduct will be a datafrane of 10 rows of characters with basic fields, name of home planet and name of director in first film in which they appear.Assume that first film with lowest API id. 

a)10 fields will be : Name, Height, Mass, Hair_color, Skin_color, Birth_year, gender, homeworld(planet), director(film)





```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



### Loading Library

1] Loading library to sent API request and parse the content 

```{r include=FALSE}
library(tidyverse) 
library(dplyr)
library(httr) #for api request
library(jsonlite) #Handling json data

```

2] Storing the data for each endpoint in different variables.Path for each endpoint is mentioned in the API documentation.Link for the StarWars API: https://swapi.dev/

```{r}
People <- "https://swapi.dev/api/people/"
Planets <- "https://swapi.dev/api/planets/"
Films <- "https://swapi.dev/api/films/"
```

### Getting the API request 

3] Building a API request and submit it. Using get function from httr package for each endpoint to get the request from the API

```{r}
request_people <- GET(People)
request_Planets <- GET(Planets)
request_Films <- GET(Films)

```

4] Check the status code for each request endpoints

Note: Status code of 200 indicates if the request is sucessfull and here we need to check if the API returned an error or not. Status code for error is 404.

```{r}
request_people$status_code
request_Planets$status_code
request_Films$status_code
```
Here we have received status code of 200 for all our endpoints.

5]Data we have received is in Json format we need to parse or handle this json data 

```{r}
request_people
```

6] Parsing the content from server to json format then converting it to dataframe format in r using rbind.

```{r}
People_json <- fromJSON(People)
People_data <- do.call(rbind, People_json)
People_data


Planet_json <- fromJSON(Planets)
Planet_data <- do.call(rbind, Planet_json)
Planet_data


Films_json <- fromJSON(Films)
Films_data <-do.call(rbind,Films_json)
Films_data
```
7] Viewing the Planet_data, People_data and Film_data dataframes
 
```{r}
View(Planet_data)
View(People_data)
View(Films_data)
```

8] In People_data dataframe we want a new column called planet id which will store the id of Planet_data dataframe, so planet id is extracted from the homeworld column which contains planet endpoint api.

Helpful link:
https://stackoverflow.com/questions/49628339/extracting-parameter-from-url-in-r
https://stackoverflow.com/questions/25991824/remove-all-characters-before-a-period-in-a-string

```{r}

People_data$PlanetId<-gsub(".*planets/","",People_data$homeworld)
People_data$PlanetId<-gsub("\\/.*","", People_data$PlanetId )

```

9] Creating a new column called planet id in Planet_data dataframe and storing the extracted id from url column in new column.

```{r}
Planet_data$PlanetId <- gsub(".*planets/", "", Planet_data$url)
Planet_data$PlanetId<-gsub("\\/.*","", Planet_data$PlanetId )
```

10] First two rows in the people dataframe id are invalid so replacing it with NA values

```{r}
People_data$PlanetId[1] <- NA
People_data$PlanetId[2] <- NA

```


11] First two rows in the planet dataframe id are invalid so replacing it with NA values


```{r}
Planet_data$PlanetId[1] <- NA  
Planet_data$PlanetId[2] <- NA  
```
### Extracting planet name from planet_data dataframe

12] Getting the matching planet name from planet_data dataframe based on planet id present in people's dataframe

Helpful Link: https://stackoverflow.com/questions/1299871/how-to-join-merge-data-frames-inner-outer-left-right


```{r}
People_data$PlanetName <- Planet_data$name[ match(People_data$PlanetId, Planet_data$PlanetId) ]


```

13] In People_data dataframe creating a new column called FilmList to store the list of flim id for each people's row. New column will contain the numberic string which is extracted from films column. The films column contain the single or list endpint api listed.
Help Link: https://stackoverflow.com/questions/14543627/extracting-numbers-from-vectors-of-strings
#argument is not an atomic vector; coercing
```{r}

People_data$FilmIdList<-sapply(People_data$films, function(x) sub('http://swapi.dev/api/films/', "",x))
People_data$FilmIdList<-gsub("\\/","", People_data$FilmIdList )

```

14] From previous step we have a  numberic list extracted from film column, now we need the first or lowest api to be extrated from this column. To do so we first create a new column called FilmId and store the first numeric character in this column for each people's row.

Helpful link:
https://stackoverflow.com/questions/21675379/r-only-keep-the-3-x-first-characters-in-a-all-rows-in-a-column

```{r}

People_data$FilmId<-gsub( "\ .*$", "", People_data$FilmIdList )
People_data$FilmId<-gsub( ".*?([0-9]+).*", "\\1", People_data$FilmId )

```

15] In Films_data dataframe we need to have filmid for each row in this dataframe. So we are extracting the id from the url column and storing it in new column named as FilmId

```{r}

#Films_data$FilmId <- gsub("[^0-9]", "", Films_data$url)
Films_data$FilmId <- gsub(".*films/", "", Films_data$url)
Films_data$FilmId <-gsub("\\/.*","", Films_data$FilmId )

```

16] First row in the film dataframe id are invalid so replacing it with NA values

```{r}
Films_data$FilmId[1] <- NA
```
### Extracting Director Name  from Films_data dataframe


17] In People_data dataframe we create a new column named as "FilmDirectorName" to store the director's name if the FilmId match is found in People_data and Films_data dataframe.

```{r}
People_data$FilmDirectorName <- Films_data$director[ match(People_data$FilmId, Films_data$FilmId)]

```

18]In People_data dataframe we need to have peopleId for each row in this dataframe. So we are extracting the id from the url column and storing it in new column named as peopleId

```{r}


People_data$Id <- gsub(".*people/", "", People_data$url)
People_data$Id<-gsub("\\/.*","", People_data$Id)
```

```{r, message=FALSE}
#passing parameters
Id<-params$Id
People_data[match(Id,People_data$Id),]

```


#### `r People_data[params$Id,1]`'s Character Sheet

#### Height: `r People_data [params$Id,2]`
#### Mass: `r People_data [params$Id,3]`
#### Hair Color: `r People_data [params$Id,4]`
#### Skin Color: `r People_data [params$Id,5]`
#### Birth Year: `r People_data [params$Id,6]`
#### Gender: `r People_data [params$Id,7]`
#### Planet Name: `r People_data [params$Id,18]`
#### Film Director Name: `r People_data [params$Id,21]`

